%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 2.0 (6/7/2019)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{article} % Default document font size

\input{structure.tex} % Include the file specifying the document structure and styling

% Set PDF meta-information
\hypersetup{
	pdftitle={Lucia Smidova - Curriculum vitae},
	pdfauthor={Lucia Smidova}
}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION
%----------------------------------------------------------------------------------------

{\LARGE\bfseries Lucia Šmídová} \\ % Name

Born: November 12, 1993---Trenčín, Slovakia\\ % Date of birth
Nationality: Slovak% Nationality

\begin{multicols}{2}
	\section*{Contact information}
	Institute of Geology and Palaeontology\\ % Address
	Faculty of Natural Sciences, Charles University\\ Albertov 6, 18200 Czech republic
	\medskip % Whitespace
	




Phone: +420 727 885 153\ % Phone number


Email: \href{mailto:smidovaluc@natur.cuni.cz}{smidovaluc@natur.cuni.cz}\\ % Email address
Personal website: \href{https://luci-netizen.github.io/personal_website/index.html}{https://luci-netizen.github.io/}\\ % Academic/personal website

\vspace{0.03\textheight} % Whitespace between contact information and specific CV information

%------------------------------------------------


%------------------------------------------------

\section*{Current position}

\emph{PhD student}, Institute of Geology and Palaeontology, Charles University % Current or most recent employment position

%------------------------------------------------

\section*{Areas of specialisation}

Paleoentomology, Fossil cockroaches, Evolution of Insects % Primary areas of research interest

\end{multicols}
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section*{Education}

\years{2018}\textsc{MSc} in Geology, Charles University, Prague\\
\years{2018- now}\textsc{PhD} in Geology, Charles University, Prague


%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND TALKS
%----------------------------------------------------------------------------------------

\section*{Publications \& conferences}

\subsection*{Journal articles}

\years{2016}Vršanský, P.V., \textbf{Šmídová, L}., Valaška, D., Barna, P., Vidlička, Ľ., Takáč, P., Pavlik, L., Kúdelová, T., Karim, T.S., Zelagin, D. and Smith, D., 2016. Origin of origami cockroach reveals long-lasting (11 Ma) phenotype instability following viviparity. The Science of Nature, 103(9), pp.1-15. \\
\years{2017}\textbf{Šmídová, L}. and Lei, X., 2017. The earliest amber-recorded type cockroach family was aposematic (Blattaria: Blattidae). Cretaceous Research, 72, pp.189-199.\\
\years{2018}Vršanský, P., Bechly, G., Zhang, Q., Jarzembowski, E.A., Mlynský, T., \textbf{Šmídová, L.}, Barna, P., Kúdela, M., Aristov, D., Bigalk, S. and Krogmann, L., 2018. Batesian insect-insect mimicry-related explosive radiation of ancient alienopterid cockroaches. Biologia, 73(10), pp.987-1006.\\
\years{2019}Vršanský, P., \textbf{Šmídová, L}., Sendi, H., Barna, P., Müller, P., Ellenberger, S., Wu, H., Ren, X., Lei, X., Azar, D. and Šurka, J., 2019. Parasitic cockroaches indicate complex states of earliest proved ants. Biologia, 74(1), pp.65-89.\\
\years{2019}Vršanský, P., Vršanská, L., Beňo, M., Bao, T., Lei, X.J., Ren, X.J., Wu, H., \textbf{Šmídová, L}., Bechly, G., Jun, L. and Yeo, M., 2018. Pathogenic DWV infection symptoms in a Cretaceous cockroach. Paleontographica Abteilung A, pp.0375-0442.\\
\years{2019}Barna, P., \textbf{Šmídová, L}. and José, M.A.C., 2019. Living cockroach genus Anaplecta discovered in Chiapas amber (Blattaria: Ectobiidae: Anaplecta vega sp. n.). PeerJ, 7, p.e7922.\\
\years{2020} \textbf{Šmídová, L}., 2020. Cryptic bark cockroach (Blattinae: Bubosa poinari gen. et sp. nov.) from mid-Cretaceous amber of northern Myanmar. Cretaceous Research, 109, p.104383.\\
\years{2021}\textbf{Šmídová L}., 2021. New genus and species of the families Olidae and Corydiidae (Corydioidea, Blattodea) from mid-Cretaceous Kachin amber. Palaentographica Abteilung A (in press)\\
\years{2021} \textbf{Šmídová L.}, Vidlička, Ľ., Wiedmann, S. 2021. Appearance of the family Blaberidae (Insecta: Blattaria) during the Cretaceous and a review of fossils of this family. Palaentographica Abteilung A (in press)\begin{flushleft}
\end{flushleft}

\subsection*{Conferences}

\years{2017} International Conference Of Young Geologists, Herlany-Dobczyce (Poland), March 30th – April 2nd 2017.\\
\years{2020} XXIst International Conference of Young Geologists 2020. 5. - 6., November 2020, Online:
Šmídová L. 2020. Cockroach fauna of mid-Cretaceous Myanmar amber as valuable insight into the phylogeny of the group [abstract].



%------------------------------------------------

\subsection*{Popularization}

\years{2016} The pop-science article about newly described species in 2015, \href{https://www.quark.sk/10-x-naj-za-rok-2015/}{“10 × NAJ za rok 2015"}, \emph{Quark}\\
\years{2017}  The pop-science article about newly described species in 2016, \href{https://www.quark.sk/10-x-naj-za-rok-2016/}{“10 × NAJ za rok 2016"}, \emph{Quark}\\
\years{2018}  The pop-science article about newly described species in 2017, \href{https://www.quark.sk/top-10-za-rok-2017/}{“Top 10 za rok 2017"}, \emph{Quark}\\
\years{2019}  The pop-science article about the extinct cockroach family Alienopteridae, \href{https://www.quark.sk/votrelci-z-jantaru/}{“Votrelci z jantáru"}, \emph{Quark}\\
\years{2021}  The website dedicated to paleontology and paleoentomology (under development) \href{https://paleoentomology.rocks/}{paleoentomology.rocks}

%----------------------------------------------------------------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------

\section*{Teaching}
\begin{itemize}
\itemsep -0.5em
\item 1 hour lesson on the Evolution of Insects as part of the Advanced Systematic Paleontology class  
 \item1/2 hour lesson on the Amber Taphonomy as part of the class Taphonomy and Lagerstatten 
\end{itemize}
-both given at the Institue of Geology and Palaeontology, Charles University
%------------------------------------------------

 %----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section*{Work experience}
\years{12/2015} Internship at the Institute of Geology and Palaeontology, Chinese Academy of Sciences, Nanjing \\
\years{8/2016} Internship at the Institute of Geology and Palaeontology, Chinese Academy of Sciences, Nanjing \\
\years{10/2017} Internship at the Institute of Geology and Palaeontology, Chinese Academy of Sciences, Nanjing \\
\years{2018-2019} Technical support representative for spanish clients at a stock exchange company \\
\years{2019-now} Creating maps for a \href{http://www.zaniklekrajiny.cz}{project} dedicated to historical demography of Czech republic

%----------------------------------------------------------------------------------------
%	SKILLS AND ABILITIES
%----------------------------------------------------------------------------------------

\section*{Skills and abilities}

\begin{multicols}{2}
\begin{itemize}
\itemsep -0.5em
\item programming with Python, HTML, CSS, JavaScript, \LaTeX 
\item creating maps with ArcGis 
\item drawing/digital drawing and painting (Adobe Fresco, Vectornator, Gimp) 
	
\end{itemize}
\end{multicols}
	\begin{barchart}{5.5}
	\baritem{Slovak}{100}
	\baritem{English}{80}
	\baritem{Spanish}{50}

\end{barchart}

\vfill % Whitespace before final footer

%----------------------------------------------------------------------------------------
%	FINAL FOOTER
%----------------------------------------------------------------------------------------

% Any final footer text such as a URL to the latest version of this CV, last updated date, compiled in XeTeX, etc
\begin{center}
	\scriptsize
	Last updated: \today~~\raisebox{-0.5pt}{\textbullet}~~ \href{https://www.LaTeXTemplates.com}{https://www.LaTeXTemplates.com}
\end{center}

%----------------------------------------------------------------------------------------

\end{document}
